

\documentclass{beamer}
\usepackage{graphicx}
\usepackage{amsmath}
\usetheme{Madrid}

\title{STAT 3611: Probability \& Statistics II Lab}
\subtitle{Semester Start Up}
\author{Kaosar}
\institute{Auburn University}
\date{Spring 2025}
\begin{document}

\frame{\titlepage}

\begin{frame}{Who am I?}
\textbf{Instructor:} Kaosar Uddin\\
\textbf{Position:} PhD Candidate in Statistics and Data Science\\
\textbf{Office:} Parker Hall 124(A)\\
\textbf{Office Hours:} TR : 1 to 2 pm or by appointment\\
\textbf{Email:} mzu0014@auburn.edu

\end{frame}
\begin{frame}{Syllabus}
\begin{itemize}
    \item Co-Requisites: STAT 3610
    \item Course Description 
    \item Course Outcomes 
    \item Instructor Objectives 
\end{itemize}
\end{frame}
 
\begin{frame}{Course Topic List}
\begin{itemize}
    \item Lab schedule aligned with STAT 3610 section by Dr. Wang.
    \item Topics from chapters 6--9 of the statistics textbook.
    \item Material matches STAT 3610 content.
\end{itemize}
\end{frame}

\begin{frame}{General Lab Overview}
\begin{itemize}
    \item Attendance is required.
    \item Labs must be completed during lab time.
    \item Instructions and submissions handled through Canvas.
    \item Structure:
    \begin{itemize}
        \item Short material overview at the start.
        \item Majority of time for assignment work.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Schedule}
\begin{itemize}
    \item No final exam!
    \item Final exam period may be used for make-up purposes.
\end{itemize}
\end{frame}

\begin{frame}{Grading}
\begin{itemize}
    \item Attendance: 5%
    \item Activity : 20 %
    \item Closed Resource Labs: 20% (Labs 5, 10)
    \item Open Resource Labs: 55% (all other labs)
\end{itemize}
\end{frame}

\begin{frame}{Software}
\textbf{R:}
\begin{itemize}
    \item One of the most commonly used statistical software.
    \item Free and open-source.
    \item Installed on lab computers.
    \item Easy to install on personal computers.
\end{itemize}
\end{frame}



\begin{frame}{Today’s Lab}
\begin{itemize}
    \item Working through swirl tutorials in R.
    \item Creating a note-sheet for future labs.
    \item Note-sheet will be expanded throughout the semester.
    \item Full instructions provided in the lab document.
\end{itemize}
\end{frame}

\end{document}
