\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{fancyhdr}

% Customizing header and footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{STAT 3611 - Spring 2025}
\fancyhead[R]{Syllabus}
\fancyfoot[C]{\thepage}

% Customizing section headings
\titleformat{\section}{\large\bfseries\color{blue}}{}{0em}{}[{\titlerule[0.8pt]}]
\titleformat{\subsection}{\normalsize\bfseries\color{blue}}{}{0em}{}

\begin{document}

\begin{center}
    \Huge \textbf{STAT 3611} \\
    \LARGE \textbf{Probability and Statistics II Lab} \\
    \Large Spring 2025 Syllabus
\end{center}

\vspace{1em}

\noindent
\textbf{Class Room:} Parker Hall 126 \\
\textbf{Class Times:} TR 3:30 - 4:45 pm \\

\noindent
\textbf{Instructor:} Kaosar Uddin \\
\textbf{Office:} Parker Hall 124(A) \\
\textbf{Office Hours:} TR 1 to 2 pm (or by appointment) \\
\textbf{E-Mail:} \href{mailto:mzu0014@auburn.edu}{mzu0014@auburn.edu} \\

\section*{CO-REQUISITES}
\begin{itemize}
    \item STAT 3610
\end{itemize}

\section*{COURSE DESCRIPTION}
STAT 3611 focuses on the application of statistical techniques taught in STAT 3610. The lab is designed to teach students the fundamentals of \textbf{R Programming} and its use in solving statistical problems.

\section*{COURSE OUTCOMES}
By the end of the semester, students will be able to:
\begin{itemize}
    \item Write error-free R code for statistical analysis.
    \item Interpret the results of statistical tests in practical contexts.
    \item Prepare professional reports that communicate statistical findings effectively.
\end{itemize}

\section*{INSTRUCTOR OBJECTIVES}
Students will:
\begin{itemize}
    \item Learn to use R for statistical problem-solving.
    \item Develop independence and teamwork skills for mastering course content.
    \item Build confidence in tackling complex problems beyond standard examples.
\end{itemize}

\section*{MATERIALS}
\begin{itemize}
    \item \textbf{Technology:}
    \begin{itemize}
        \item Lab computers with required software will be available during class.
        \item Students may install R on their personal computers.
    \end{itemize}
    \item \textbf{Textbook:} \emph{Probability and Statistical Inference}, 10th edition by Hogg and Tanis. \\
    The same textbook is used for STAT 3610. Students who have not opted out of the all-access book will find it in their STAT 3610 Canvas course.
    \item Follow all course announcements on Canvas and in class.
\end{itemize}

\section*{ASSIGNMENTS \& ACTIVITIES}
\begin{itemize}
    \item Attendance in lab is required. Students must be present to submit lab work for a grade.
    \item Each lab includes a programming component and a written report.
    \item Labs may be open or closed note/resource. Specific instructions will be provided.
\end{itemize}

\section*{MAKE-UPS \& RE-GRADES}
\begin{itemize}
    \item Notify the instructor at least two weeks in advance for Auburn-approved absences.
    \item Documentation for excused absences must be submitted through \href{https://aub.ie/EngAbsence}{aub.ie/EngAbsence}.
    \item Regrade requests must be submitted within one week after the assignment is returned. Requests apply to the entire assignment.
    \item Makeup labs are guaranteed only for university-excused absences.
\end{itemize}

\section*{GRADING}
\begin{center}
\begin{tabular}{|l|l|}
\hline
\textbf{Semester Grade Weights} & \textbf{Percentage} \\ \hline
Attendance & 5\% \\ \hline
Activity & 20\% \\ \hline
Closed Resource Labs & 20\% \\ \hline
Open Resource Labs & 55\% \\ \hline
\end{tabular}

\vspace{1em}

\begin{tabular}{|l|l|}
\hline
\textbf{Final Grades} & \textbf{Percentage Range} \\ \hline
A & 89.5\% - 100\% \\ \hline
B & 79.5\% - 89.4\% \\ \hline
C & 69.5\% - 79.4\% \\ \hline
D & 59.5\% - 69.4\% \\ \hline
F & Below 59.5\% \\ \hline
\end{tabular}
\end{center}

\section*{COMMUNICATION \& QUESTIONS}
\begin{itemize}
    \item Use your official Auburn email with the subject line starting with \texttt{[STAT 3611]}.
        \item Questions that are related to course content or apply to the whole class should be posted in the Canvas Discussions. Questions submitted by email that apply to the whole class may be answered only on the Canvas Discussions. Individual or personal questions should be submitted via email
\end{itemize}

\section*{ACADEMIC HONESTY}
All participants are expected and required to abide by the \href{http://www.auburn.edu/academic/provost/academicHonesty.php}{Auburn University Academic Honesty Code}.

\section*{ACCOMMODATIONS}
Students who require accommodations should submit their approved accommodations through AU Access and meet with the instructor within the first week of class (or as soon as possible after the accommodation becomes necessary).

\begin{itemize}
    \item I want you to have all the resources that are necessary and reasonable for you to succeed in this class. It is your responsibility to meet with me individually before any accommodations need to go into effect. We will work to put everything in place for all assignments and assessments occurring after our meeting.
    \item Even if you are not planning on using your accommodation this semester, please schedule a short meeting with me so that we can go over what accommodations are available for you so that they can be put into place quickly should you change your mind about using them during the semester.
    \item If you have not yet set up your necessary accommodations through the Office of Accessibility, make an appointment with the Office of Accessibility (1228 Haley Center, 844-2096).
\end{itemize}

\section*{HEALTH AND SAFETY}
\begin{itemize}
    \item Notify the instructor promptly if you become ill.
    \item In response to COVID-19, Auburn University permits individual faculty members to require face coverings in their classrooms. While we will not start the semester with a face covering requirement for regular class attendance, the course policy may change during the semester. If the course policy changes, students in this class will be required to wear face coverings that appropriately cover the nose and mouth to limit the spread of infectious disease for ALL in-person activities. Any changes to the course face covering policy will be announced in class and on Canvas.
\end{itemize}

\section*{OTHER EXPECTATIONS}
\begin{itemize}
    \item Mutual respect is expected from all participants.

    \item It is my intent that students from all diverse backgrounds and perspectives be well served by this course, that students’ learning needs be addressed both in and out of class, and that the diversity that students bring to this class be viewed as a resource, strength, and benefit.
    \item It is my intent to present materials and activities that are respectful of diversity: gender, religion, sexuality, disability, age, socioeconomic status, veteran status, ethnicity, race, and culture.
    \item All students in this course are expected to respect their fellow classmates and actively participate in fostering an inclusive learning environment.
    \item Your suggestions are encouraged and appreciated. Please let me know ways to improve the
    effectiveness of the course for you personally or for other students or student groups.
  
\end{itemize}
\vspace{1em}
\noindent
\textbf{Note:} This syllabus is subject to change at the instructor’s discretion. All changes will be communicated in class or on Canvas.

\end{document}
