\documentclass{beamer}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{xcolor}
\usetheme{Madrid}

\title[STAT 3611]{Week 14: One-Way ANOVA (Final Lab)}
\author{Kaosar}
\institute{Auburn University}
\date{Spring 2025}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Administrative Items}
\begin{itemize}
    \item Use your note sheet, old labs, and resources during open lab.
    \item \textbf{This is the last lab of the semester.}
    \item \textbf{No class during finals week.}
    \item Do not use code generators — write your own R code.
    \item Looking up syntax/documentation is allowed.
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Subsetting a Data Frame in R}
\textbf{Using the \texttt{ToothGrowth} dataset:}
\begin{verbatim}
data("ToothGrowth")

# Subset to include only rows with "OJ"
ToothGrowth[ToothGrowth$supp == "OJ", ]

# Select specific columns (e.g., first and second)
ToothGrowth[ToothGrowth$supp == "OJ", c(1,2)]
\end{verbatim}
\end{frame}

\begin{frame}{Introduction to One-Way ANOVA}
\begin{itemize}
    \item ANOVA = \textbf{Analysis of Variance}
    \item Used to compare \textbf{three or more group means}.
    \item \textbf{H\textsubscript{0}}: \( \mu_1 = \mu_2 = \mu_3 = \cdots = \mu_m \)
    \item \textbf{H\textsubscript{1}}: At least one mean is different.
    \item \textbf{m}: number of independent groups
    \item \textbf{n}: total number of observations
\end{itemize}
\end{frame}

\begin{frame}{Decision Rule for ANOVA}
\begin{itemize}
    \item Use the \textbf{F-ratio} from ANOVA output.
    \item Compare with critical value from F-table:
    \[ \text{Reject } H_0 \text{ if } F_{\text{ratio}} > F_{\text{table}} \]
    \item Find critical values: \url{https://www.statology.org/f-distribution-table/}
\end{itemize}
\end{frame}

\begin{frame}[fragile]{Conducting ANOVA in R}
\textbf{Steps to perform one-way ANOVA:}
\begin{verbatim}
# Step 1: Load data and run the test
anovaResults <- aov(len ~ supp, data = ToothGrowth)

# Step 2: Print the ANOVA summary
summary(anovaResults)
\end{verbatim}
\end{frame}

\begin{frame}[fragile]{Example Output}
\textbf{Typical ANOVA output:}
\begin{verbatim}
             Df Sum Sq Mean Sq F value Pr(>F)
supp          1  205.4  205.35   15.57  0.0002
Residuals    58  764.0   13.17
\end{verbatim}
\textbf{Interpretation:}
\begin{itemize}
    \item p-value = 0.0002 $<$ 0.05 → reject \( H_0 \)
    \item Conclusion: supplement type has a significant effect on tooth length
\end{itemize}
\end{frame}

\begin{frame}{Lab Submissions}
\begin{itemize}
    \item Submit a clearly commented R script that runs without error.
    \item Submit a report using the template provided on Canvas.
    \item Add brief summaries and interpretations where required.
    \item Submit updated note sheet as required.
\end{itemize}
\end{frame}

\end{document}